On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-05-09 manuscripts/IEEE/final_submission.tex
final edits
open problems

We close with some remaining open challenges.  First, there is the basic problem of proving optimal lower bounds on sufficient sample size guaranteeing uniqueness and stability in sparse coding.  Additionally, given the NP-hardness of verifying spark conditions for matrices, are the corresponding approximation Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} also computationally hard?  In what special cases is it efficient to check that a solution is stably unique for these problems?  Finally, as $\ell_1$ relaxations for inferring sparse vectors have, in many cases \cite{eldar2012compressed}, the same solutions as for $\ell_0$, is there an $\ell_1$ version of Thm.~\ref{SLCopt}?  % [*** Incorporate this open problem with more words ***]

>>>>

We close with some challenges left open by our work. First, there is the basic problem of proving optimal lower bounds on sufficient sample size $N$ guaranteeing the uniqueness and stability of sparse representations. The pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} is loose in that it assigns to each support $S \in \mathcal{H}$ a corresponding support $\overline S$ without consideration of previously matched pairs; although we doubt tightening in this way will lead to sub-exponential sample sizes. Sample complexity will also benefit from lowering the number of required supports, i.e. the size of regular uniform hypergraphs satisfying the SIP. The regularity requirement on support hypergraphs can be loosened to allow for certain non-regular hypergraphs satisfying constraints on the degree sequence of nodes; though we impose regularity for clarity of exposition. It is then natural to ask: what is the smallest hypergraph satisfying the required constraints forgiven $m$ and $k$? Finally, the error bounds can be improved by tightening the constant $C_1$, e.g. via an improvement in Lemma ?.

Additionally, given the NP-hardness of verifying spark conditions for matrices, are the corresponding approximation Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} also computationally hard?  In what special cases is it efficient to check that a solution is stably unique for these problems?  Finally, as $\ell_1$ relaxations for inferring sparse vectors have, in many cases \cite{eldar2012compressed}, the same solutions as for $\ell_0$, is there an $\ell_1$ version of Thm.~\ref{SLCopt}?  % [*** Incorporate this open problem with more words ***]
